---
title: "Spatial data management and geodesy"
author: |
  | Deependra Dhakal
  | Assistant Professor
  | \textit{ddhakal.rookie@gmail.com}
  | \url{https://rookie.rbind.io}
output: 
  binb::monash:
    toc: true
    keep_tex: true
    slide_level: 2
    includes:
      in_header: beamer_header_template.tex
colortheme: monashwhite
outertheme: smoothtree
innertheme: rounded
innercolortheme: rose
outercolortheme: whale
linkcolor: red
urlcolor: lightgrayd
# titlefontsize: 22pt # breaks custom \lineskip
titlepage: falcon.png
fontsize: 11pt
classoption: "aspectratio=169" # "compressed"
bibliography: [./../bibliographies.bib]
header-includes: 
  - \AtBeginSubsection{}
---

```{r setup, include=FALSE}
library(knitr)
require(tidyverse)
require(sf)
require(sp)

set.seed(453)
# invalidate cache when the package version changes
knitr::opts_chunk$set(tidy = FALSE, echo = FALSE, 
                  message = FALSE, warning = FALSE,
                  out.width = "45%", cache = TRUE, 
                  dev.args=list(bg=grey(0.9), pointsize=11))
options(knitr.table.format = "latex")
options(knitr.kable.NA = "", digits = 2)
options(kableExtra.latex.load_packages = FALSE)
theme_set(theme_bw())
```

# Infrared imagery

##

```{r}
# source literature: https://www.e-education.psu.edu/meteo3/l5_p5.html
# source data: https://www.e-education.psu.edu/meteo3/sites/www.e-education.psu.edu.meteo3/files/images/lesson5/ir_fog0308.png
```

## ARGOS-4

literature source: https://www.nesdis.noaa.gov/next-generation/argos-4-launch
ARGOS-4 launch is set for September 29, 2022

Once in orbit, Argos-4 will join a network of other Argos instruments onboard other polar orbiting satellites to collect a variety of data from both stationary and mobile transmitters around the world. This vital information helps provide a better understanding of Earth’s physical and biological environment, including its weather and climate, biodiversity and ecosystems, as well as assist with maritime security, offshore pollution, and humanitarian assistance.

## Free gis data

https://freegisdata.rtwilson.com/

# Introduction to geospatial data

## Spatial dataset: An example

```{r example-data}
p1 = st_point(c(7,52))
p2 = st_point(c(-30,20))

# let's set the projection to longlat with WGS84, epsg code 4326
sfc = st_sfc(p1, p2, crs = 4326) # crs is equivalent to "+init=epsg:4326 +proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+towgs84=0,0,0"; this information is obtained with
# CRS("+init=epsg:4326")

# # setting crs is done by
sfc %>% 
  st_transform(crs = "+init=epsg:3857") # mercator projection, google maps/osm maps tiles

sfc %>% 
  st_transform(crs = "+init=epsg:4269") # longlat projection with NAD83

ggplot() +
  geom_sf(data = st_geometry(sfc)) +
  theme_minimal() +
  coord_sf(crs = "+init=epsg:3857")
```

##

https://erinbecker.github.io/r-raster-vector-geospatial/aio.html

# Bibliography

## References
